---
title: "Python flair!"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(reticulate)
library(tidyverse)
library(flair)
```

## Python in `.Rmd` files

### Load libraries

Just like R, you can use Python in `.Rmd` files! Here we `import` our libraries

```{python libraries, include=FALSE}
import pandas as pd
```

```{r, echo = FALSE}
decorate("libraries") %>% 
  flair("import")
```

### Load data

Let's use `pd.read_csv` to load the titanic data and view the top of the data set:

```{python data, include=FALSE}
titanic  = pd.read_csv("data/titanic.csv")
titanic.head()
```

```{r, echo = FALSE}
decorate("data") %>% 
  flair("pd.read_csv", background = "pink")
```

### plot data

Passing the python data frame into `ggplot` using `py$data_frame` syntax to make my scatterplot (what can I say, I love `ggolot2`...).

```{r plot, warning=FALSE, fig.height=4, fig.width=4, include=FALSE}
ggplot2::ggplot(py$titanic, aes(x = age, y = fare)) +
  geom_point()
```

```{r, echo = FALSE}
decorate("plot") %>% 
  flair("ggplot(py$titanic, aes(x = age, y = fare))", background = "pink") %>% 
  flair("py$titanic", color = "CornflowerBlue")
```

### And inline python code within markdown text!

Here we find the destination of the first passenger:

```{python first destination, include=FALSE}
first_dest = titanic["home.dest"][0]
```

```{r, echo = FALSE}
decorate("first destination") %>% 
  flair('titanic["home.dest"][0]', background = "yellow")
```

The destination of the first passenger is `r py$first_dest`.
